---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r echo=TRUE}
data <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?

### Total number of steps per day
```{r echo=TRUE}
aggregate(data$steps, by=data["date"], sum, na.rm=T)
```


### Histogram of total number of steps per day
```{r echo=TRUE}
steps_per_day <- tapply(data$steps,data$date,sum)
hist(steps_per_day, col="blue")
```


### Summary of total number of steps per day
```{r}
steps_summary <- summary(steps_per_day)
steps_summary
```


The mean and median of the total number of steps per day is `r steps_summary["Mean"]` and `r steps_summary["Median"]` respectively.


## What is the average daily activity pattern?


### Plot of average daily activity
```{r echo=TRUE}
avg_daily_steps <- tapply(data$steps,data$interval,mean,na.rm=T)
plot(avg_daily_steps, type="l", ylab="Average daily steps", xlab="5 minute interval", main="Average daily activity pattern")
```


### Interval with max average steps
```{r echo=TRUE}
max_steps <- max(avg_daily_steps)
interval_max <- names(avg_daily_steps[which(avg_daily_steps == max_steps)])

```

`r interval_max`th interval has the maximum number of aaverage steps taken across all the days is the dataset with value of `r max_steps` steps.



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
